Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \acp{isms}.

### 2017-04-01 msbframework/msbintro/msbintro.tex
Translated lecture to english. Updated the MSB statutes to 2016:1

\title[Intro MSB]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) support for introducing \acp{isms}.
}
\author{Carina Bengtsson, Daniel Bosk and Lennart Franked\footnote{%
  Detta verk är tillgängliggjort under licensen Creative Commons 
  Erkännande-DelaLika 2.5 Sverige (CC BY-SA 2.5 SE).
	För att se en sammanfattning och kopia av licenstexten besök URL 
	\url{http://creativecommons.org/licenses/by-sa/2.5/se/}.
}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.

@@

\begin{frame}{MSB}
  \begin{itemize}
    \item Swedish Civil Contingencies Agency (MSB).
    \item \enquote{MSB is responsible for issues concerning civil protection,
        public safety, emergency management and civil defence, as long as no
        other authority has responsibility\cite[About MSB]{msbse}.
        .}
  \end{itemize}
\end{frame}

>>>>

\title[Intro MSB]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \acp{isms}.
}
\author{Carina Bengtsson, Daniel Bosk and Lennart Franked\footnote{%
  Detta verk är tillgängliggjort under licensen Creative Commons 
  Erkännande-DelaLika 2.5 Sverige (CC BY-SA 2.5 SE).
	För att se en sammanfattning och kopia av licenstexten besök URL 
	\url{http://creativecommons.org/licenses/by-sa/2.5/se/}.
}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.

@@

\begin{frame}{MSB}
  \begin{itemize}
    \item Swedish Civil Contingencies Agency (MSB).
    \item \enquote{MSB is responsible for issues concerning civil protection,
        public safety, emergency management and civil defence, as long as no
        other authority has responsibility\cite[About MSB]{msbse}\@.
        .}
  \end{itemize}
\end{frame}
